Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2020-02-27 write-up/fda-recurrent.tex
Doing asymp normality now

@@

\begin{proof}[Proof of Asymptotic Normality]
Consider the weighted estimating equations given by~\eqref{eq:approxscore}. We have shown that afjlakfjlakfj
Then
\end{proof}

>>>>

\label{eq:decomp}

@@

\begin{proof}[Proof of Asymptotic Normality]
Consider a Taylor-expansion of $\tilde U_n (\theta)$ centered at $\theta_0$ when $\hat \theta_n \in \Theta_0$.  We can write as
\begin{align*}
\tilde U_n (\hat \theta_n) &= \tilde U_n (\theta_0) -  (\hat \theta_n - \theta_0) \frac{\partial}{\partial \theta} \tilde U_n (\theta) \mid_{\theta=\theta_0} - (\hat \theta_n - \theta_0) \sum_{l=1}^p (\hat \theta_{ln} - \theta_{l0}) \frac{\partial^2}{\partial \theta \partial \theta_l} \tilde U_n (\theta) \mid_{\theta=\theta^\star} \\
0 &= \tilde U_n (\theta_0) + (\hat \theta_n - \theta_0) \left[ \frac{\partial}{\partial \theta} \tilde U_n (\theta) \mid_{\theta=\theta_0} + (\hat \theta_n - \theta_0)^2 \frac{\partial}{\partial \theta} \tilde U_n (\theta) \mid_{\theta=\theta^\star} \right] \\
\end{align*}
where~$\theta^\star$ s on the line segment between $\hat \theta_n$ and $\theta_0$.

Now $\tilde U_n (\theta_0 )$ can be decomposed into three terms as in~\eqref{eq:decomp}. Here, we assume $K_x \to \infty$ so the only two terms are
$$
U_n (\theta_0) = \sum_{i=1}^n
$$ and
$$
n^{-1} (\hat U_n - U_n (\theta_0) ) = \frac{1}{n} \sum_{i=1}^n \int_0^\tau \frac{h^{(1)}(s; \theta_0)}{\pi_i (s) + h(s; \theta_0)} dM_i (s)
$$
\end{proof}
